---
title: "Introduction to the Tidyverse"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
    df_print: default
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
tutorial_options(exercise.timelimit = 60)
```

## Welcome

This tutorial will teach you how to understand data with the Tidyverse. We will be begin by looking at dplyr and ggplot2.

### Load data

```{r data}
all_data <- readRDS("data/all_data.RDS")
```

## dplyr

dplyr is a grammar of data manipulation, providing a consistent set of verbs that help you solve the most common data manipulation challenges:

### Select

```{r select, exercise = TRUE}
select(all_data, year, month, age, term_deposit)
```

<div id="mpg-hint">
**Hint:** Type `select(...)` and then click the blue button.
</div>

```{r select-check, echo = FALSE}
# checking code
```

### Filter

```{r filter, exercise = TRUE}
filter(all_data, month == "dec")
```

### Mutate

```{r filter-check, exercise = TRUE}
mutate(all_data, log_age = log(age))
```

## ggplot

### Density

```{r plot1, exercise = TRUE}
ggplot(all_data, aes(age)) +
  geom_density()
```

<div id="help-hint">
**Hint:** Type `ggplot(...)` and then click the blue button.
</div>

```{r plot1-check, echo = FALSE}
# checking code
```

### With groups

```{r plot2, exercise = TRUE}
ggplot(all_data, aes(age, color = term_deposit)) +
  geom_density()
```

<div id="help-hint">
**Hint:** Type `ggplot(...)` and then click the blue button.
</div>

```{r plot2-check, echo = FALSE}
# checking code
```

## Exercises

```{r quiz1, echo = FALSE}
quiz(caption = "Use the code chunk above to help answer these questions.",
  question("What verb do you use to create new features?",
           answer("select"), 
           answer("filter"),
           answer("mutate", correct = TRUE),
           incorrect = "Hint: Creating new features involves changing your data.", 
           allow_retry = TRUE
  ),
  question("What command determines the visual properties in a ggplot?",
           answer("geom"), 
           answer("aes", correct = TRUE),
           answer("ggplot"),
           incorrect = "Hint: Aesthetics is another name for visual properties.", 
           allow_retry = TRUE
  ),
  question("Which items are valid geometries?",
           type = "multiple",
           answer("map"), 
           answer("point", correct = TRUE),
           answer("density", correct = TRUE),
           incorrect = "Hint: Geometries are used to plot your data.", 
           allow_retry = TRUE
  )
)
```

### Congratulations

You've now met some basic dplyr verbs and ggplot2 commands.